Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2014-12-16 nips2015.tex
more enh wip

Each point $z \in Q_k$ are called \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
\begin{equation}
  \beta_k(h, c) := \begin{cases}
    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
    0, &\mbox{Otherwise}.
  \end{cases}
\end{equation}

>>>>

Each point $z \in Q_k$ are called \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
\begin{equation}
  \beta_k(h, c) := \begin{cases}
    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
    0, &\mbox{Otherwise}.
  \end{cases}
\end{equation}
